Nail: A practical tool for parsing and generating data formats

### 2014-09-17 paper/osdi14/fig-motivation.tex
some minor typesetting
Poster first shot

\begin{figure*}
\centering
\begin{tabular}{lllr}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption & CVE-2013-5660 & Buffer overflow & 11\\
  Parsing inconsistency & CVE-2013-1462 & Multiple virus scanners interpret ZIP files incorrectly & 4\\
  Semantic misunderstanding & CVE-2014-2319 & Weak cryptography used even if user selects AES & 1\\
\midrule
  \multicolumn{3}{l}{\bf Total of all vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

\end{tabular}
\caption{Classification of vulnerabilities in the CVE database
from 2010 to May 2014 containing the term ``ZIP'' and involving
the ZIP file format.}
\label{fig:motivation} 
\end{figure*}

>>>>

\begin{figure*}
\centering
\smaller[0.5]
\input{table-motivation.tex}
\caption{Classification of vulnerabilities in the CVE database
from 2010 to May 2014 containing the term ``ZIP'' and involving
the ZIP file format.}
\label{fig:motivation} 
\end{figure*}
